Sensitivity Analysis

### 2024-05-14 SFE_article_Sensitivity_Analysis_short - Chamomile/Article_Sensitivity_Analsysis_short-Chamomile.tex
14.05

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study aimed to investigate the supercritical extraction process of caraway oil from chamomile flowers. The distributed-parameter model describes the fluid-solid extraction process. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated from the Peng-Robinson equation of state. A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s. Sensitivity analyses play a crucial role in assessing the robustness of the findings or conclusions based on mathematical model. The local sensitivity analysis investigates the influence of infinitely small changes in the inlet temperature, pressure, and flow rate on the extraction yield.

>>>>

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study aimed to investigate the supercritical extraction process of caraway oil from chamomile flowers. The distributed-parameter model describes the fluid-solid extraction process. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated from the Peng-Robinson equation of state. A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s. Sensitivity analyses play a crucial role in assessing the robustness of the findings or conclusions based on mathematical model. The local sensitivity analysis investigates the influence of infinitely small changes in the inlet temperature, pressure, and flow rate on the extraction yield.

### 2024-05-14 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Sensitivity_Pressure.tex
14.05

	As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates at the speed of sound relative to the flow. If the flow velocity is relatively low, all pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic. The Low Mach-number assumption leads to instant propagation of the thermodynamic pressure throughout the system. This assumption allows considering a single pressure value for the entire system, as all changes occur simultaneously within the machine. Figure \ref{fig:Sensitivty_P_P} illustrates a step function representing the pressure change.

@@

	The pressure change influences the temperature of the fluid in the middle of the computational domain, but the values on boundaries can be defined in multiple ways. Applying the Dirichlet boundary conditions assumes a fixed temperature value at the inlet, which leads to a possible thermal gradient propagating along the system. In contrast, Neumann boundary conditions would dictate that the heat flux at the boundaries be held constant. In this work, the Neumann boundary conditions have been applied, which leads to a uniform response and ensures the temperatures at the inlet and in the middle of the extractor are the same.

>>>>

	As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates at the speed of sound relative to the flow. If the flow velocity is relatively low, all pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic. The Low Mach-number assumption leads to instant propagation of the thermodynamic pressure throughout the system. A single pressure value can be considered for the entire system, as all changes occur simultaneously throughout the machine. Figure \ref{fig:Sensitivty_P_P} illustrates a step function representing the pressure change.

@@

	The pressure change influences the temperature of the fluid in the middle of the computational domain, but the values on boundaries can be defined in multiple ways. Applying the Dirichlet boundary conditions assumes a fixed temperature value at the inlet, which leads to a possible thermal gradient propagating along the system. In contrast, Neumann boundary conditions would dictate that the heat flux at the boundaries be held constant. In this work, the Neumann boundary conditions have been applied, which leads to a uniform response and ensures that the temperatures at the inlet and in the middle of the extractor are the same.
